VOI-aware Monte-Carlo Sampling in Trees

### 2011-12-12 paper/vago/paper.tex
fixes
corrections per eyal requests

\newtheorem{dfn}{Definition}
\newtheorem{thm}{Theorem}
\newtheorem{lmm}{Lemma}

@@

The simple regret of a sampling policy for the Multi-armed Bandit
Problem is the expected difference between the best expected reward
$\max\limits_i\IE[X_i]$ and the expected reward $\IE[X_j]$ of the arm
with the best sample mean $\overline X_j=\max\limits_i\overline X_i$:
\begin{equation}
\label{eqn:simple-regret}
\IE[R]=\sum_{j=1}^K\Delta_j\Pr(\overline X_j=\max_i\overline X_i)
\end{equation}
where $\Delta_j=\max\limits_i\IE[X_i]-\IE[X_j]$.  Strategies that
minimize the simple regret are called pure exploration strategies
\cite{Bubeck.pure}. Principles of rational metareasoning
\cite{Russell.right} suggest that at each step the arm with the great
value of information (VOI) must be pulled, and the sampling must be
stopped and a decision must be made when no arm has positive VOI.

@@

The probabilities in equations (\ref{eqn:thm-vopi}, \ref{eqn:thm-be})
can be bounded from above using concentration inequalities. In
particular, Lemma~\ref{lemma:hoeffding-prob-bounds} (proved in 
Appendix~\ref{app:hoeffding-prob-bounds-proof}) is based on the
Hoeffding inequality (\ref{eqn:conc-hoeffding}):
\begin{lmm} The probabilities in equations (\ref{eqn:thm-vopi},
\ref{eqn:thm-be}) are bounded from above as
\begin{eqnarray}
\Pr(\IE[X_i] \le \overline X_\beta|i=\alpha)&
   \le & \exp(-2 (\overline X_i - \overline X_\beta)^2 n_i)\nonumber\\
\Pr(\IE[X_i] \ge \overline X_\alpha|i\ne\alpha)&
   \le & \exp(-2 (\overline X_\alpha - \overline X_i)^2 n_i)
\label{eqn:probound-perf-hoeffding}
\end{eqnarray}
\vspace{-1.5\baselineskip}
\begin{eqnarray}
\Pr(\overline X_i' \le \overline X_\beta|i=\alpha) &
   \le & 2\exp\left(- 2\left(\frac {1+\frac {n_i} N} {1+\sqrt {\frac {n_i} N}}(\overline X_i - \overline X_\beta)\right)^2 n_i \right)
   \le 2\exp\left(- 1.37(\overline X_i - \overline X_\beta)^2 n_i \right) \nonumber\\
\Pr(\overline X_i' \ge \overline X_\alpha|i\ne\alpha) &
   \le & 2\exp\left(- 2\left(\frac {1+\frac {n_i} N} {1+\sqrt {\frac {n_i} N}} (\overline X_\alpha - \overline X_i)\right)^2 n_i \right)
    \le 2\exp\left(- 1.37(\overline X_\alpha - \overline X_i)^2 n_i \right)
\label{eqn:probound-blnk-hoeffding}
\end{eqnarray}
\label{lemma:hoeffding-prob-bounds}
\end{lmm}

An upper bound on the intrinsic value of perfect information is obtained by substituting
(\ref{eqn:probound-perf-hoeffding}) into (\ref{eqn:thm-vopi}):
\begin{equation}
  \Lambda_i^p \le \hat\Lambda_i^p=\left\{
  \begin{array}{l l}
    \overline X_\beta\cdot \exp\left(- 2(\overline X_i - \overline X_\beta)^2 n_i \right) & \mbox{{\rm if} $i=\alpha$} \\
    (1-\overline  X_\alpha)\cdot \exp\left(- 2(\overline X_\alpha - \overline X_i)^2 n_i \right)  &  \mbox{\rm otherwise}
  \end{array} \right.
\label{eqn:bound-perf-hoeffding}
\end{equation}
An upper bound on the blinkered VOI estimate with ordering independent of $N$ is obtained
by substituting (\ref{eqn:probound-blnk-hoeffding}) into (\ref{eqn:thm-be}).
\begin{equation}
  \Lambda_i^b \le \hat\Lambda_i^b=\left\{
  \begin{array}{l l}
    N\frac {\overline X_\beta} {n_i}\cdot 2\exp\left(- 1.37(\overline X_i - \overline X_\beta)^2 n_i\right)
      & \mbox{{\rm if} $i=\alpha$} \\
    N\frac {(1-\overline  X_\alpha)} {n_i}\cdot 2\exp\left(- 1.37(\overline X_\alpha - \overline X_i)^2 n_i\right)
      &  \mbox{\rm otherwise}
  \end{array} \right.
\label{eqn:bound-blnk-hoeffding}
\end{equation}
The bound is generally tighter when $N$ is small relative to $n_i$,
and the estimate $\hat\Lambda_i^b$ can be viewed as a relaxation of the myopic VOI
estimate to longer sequences of actions, such
that the VOI estimate is positive for some of the actions.

Better bounds can be obtained through tighter estimates on the
probabilities, for example, based on the empirical Bernstein inequality
(\ref{eqn:conc-empbernstein}) or through a more careful application of
the Hoeffding inequality (Appendix~\ref{app:better-hoeffding-bound}).

@@

Monte-Carlo tree search \cite{Chaslot.montecarlo} selects at each
search step an action that appears to be the best based on outcomes
of \textit{search rollouts}. Two different criteria are employed in
action selection during a rollout:
\begin{itemize}
\item at the first step, the simple regret of selecting an action
must be minimized;
\item starting with the second step of a rollout, the expected reward
of the rollout
 must be made as close as possible to the optimum reward, so that the
 value of the action at the first step of the rollout is evaluated
 correctly. Thus, starting with the second step, the cumulative regret
 must be minimized.
\end{itemize}

@@

The experiments compare the UCT algorithm \cite{Kocsis.uct} with modified
versions of UCT in which the samples at the first step are selected according
to their VOI estimates. Three blinkered VOI estimates were used for the comparison:
\begin{description}
\item[VCT:] based on Hoeffding inequality (\ref{eqn:conc-hoeffding});
\item[ECT:] based on Hoeffding inequality with midpoint (see Appendix~\ref{app:better-hoeffding-bound});
\item[BCT:] based on empirical Bernstein inequality (\ref{eqn:conc-empbernstein}).
\end{description}
For simplicity, the bounds on probability for unlimited number of samples were used in the estimate formulas. The estimates where computed as follows:
\begin{eqnarray}\
  \Lambda_i^{VCT}& =&\left\{
  \begin{array}{l l}
    \frac {\overline X_\beta} {n_i} \cdot \exp\left(- 2(\overline X_i - \overline X_\beta)^2 n_i\right)
      & \mbox{{\rm if} $i=\alpha$} \\
    \frac {(1-\overline  X_\alpha)} {n_i}\cdot \exp\left(- 2(\overline X_\alpha - \overline X_i)^2 n_i\right)
      &  \mbox{\rm otherwise}
  \end{array}  \right.\nonumber\\
  \Lambda_i^{ECT}& =&\min\left(\Lambda_i^{VCT}, \min_y\left\{
  \begin{array}{l l}
    \frac {\overline X_\beta-y} {n_i}\cdot \exp\left(-2 (\overline X_i-\overline X_\beta)^2n_i\right)
    +\frac {\overline X_\beta} {n_i}\cdot \exp\left(-2 (\overline X_i-y)^2n_i\right)
      & \mbox{{\rm if} $i=\alpha$} \\
\frac {y-\overline X_\alpha} {n_i}\cdot \exp\left(-2(\overline X_\alpha-\overline X_i)^2n_i\right)
    +\frac {1-\overline X_\alpha} {n_i}\cdot \exp\left(-2 (y-\overline X_i)^2n_i\right)
      &  \mbox{\rm otherwise}
  \end{array} \right.\right) \nonumber\\
  \Lambda_i^{BCT}& =&\min\left(\Lambda_i^{VCT},\left\{
  \begin{array}{l l}
    \frac {\overline X_\beta} {n_i}\cdot 2\exp\left(- \frac {(\overline X_i - \overline X_\beta)^2 n_i} {\frac {14} 3 \frac {n_i} {n_i-1}(\overline X_i - \overline X_\beta) + 2 \overline X_i(1-\overline X_i)} \right)
      & \mbox{{\rm if} $i=\alpha$} \\
    \frac {(1-\overline  X_\alpha)} {n_i}\cdot 2\exp\left(- \frac {(\overline X_\alpha - \overline X_i)^2 n_i} {\frac {14} 3 \frac {n_i} {n_i-1}(\overline X_\alpha - \overline X_i) + 2 \overline X_i(1-\overline X_i)} \right)
      &  \mbox{\rm otherwise}
  \end{array} \right.\right)
\label{eqn:emp-estimates}
\end{eqnarray}

@@

One search domain in which Monte-Carlo tree search based on the UCT
sampling policy has been particularly successful is playing the Go
game \cite{Gelly.mogo}. This series of experiments compares
the winning rate of UCT against VOI-aware policies (VCT, ECT, BCT)
in Go and investigates the effect of early stopping and sample
redistribution.

@@

\begin{figure}[t]
\centering
\includegraphics[scale=0.8]{bests-bw.pdf}
\caption{Go: best winning rate comparison}
\label{fig:best-winning-rate}
\end{figure}
Figure~\ref{fig:best-winning-rate} presents relative performance of
different VOI-aware policies depending on the number of samples per
ply by comparing the best achieved winning rates against UCT (again,
the lower the bar, the better is the policy). Both ECT (based on the
Hoeffding inequality with midpoint) and BCT (based on the empirical
Bernstein inequality) are better than VCT. The difference between ECT
and VCT is most prominent for smaller number of samples, and the
winning rate of ECT increases relatively slowly with the number of
samples. In contrast, BCT is worse than ECT and only slightly better
than VCT for smaller number of samples, but the winning rate rapidly
increases with the number of samples, and for 10000 and 15000 samples
per ply BCT is the best of the policies with the winning rate reaching
67\%.

@@

\section{Proof of Lemma~\ref{lemma:hoeffding-prob-bounds}}
\label{app:hoeffding-prob-bounds-proof}

@@

Bounds (\ref{eqn:bound-perf-hoeffding}, \ref{eqn:bound-blnk-hoeffding}) have the form
\begin{equation}
  \Lambda_i \le \hat\Lambda_i=\left\{
  \begin{array}{l l}
    (\overline X_\beta-B)\exp\left(- \gamma(\overline X_i - \overline X_\beta)^2 n_i \right) & \mbox{{\rm if} $i=\alpha$} \\
    (A-\overline  X_\alpha)\exp\left(- \gamma(\overline X_\alpha - \overline X_i)^2 n_i \right)  &  \mbox{\rm otherwise}
  \end{array} \right.
\label{eqn:bound-generic-hoeffding}
\end{equation}
where $A$ is the upper bound on the posterior sample mean $\overline X_i'$ if $i\ne \alpha$, $B$ is the lower bound on $\overline X_i'$ if $i=\alpha$. For $i=\alpha$, the bound can be improved by selecting a midpoint
$B < y < \overline X_\beta$ and computing the bound as the sum of two parts:
\begin{itemize}
\item $\overline X_\beta-y$ multiplied by the probability that
  $\overline X_i' \le \overline X_\beta$;
\item $\overline X_\beta-B$ multiplied by the probability that $\overline X_i'\le
  y$.
\end{itemize}.
\begin{equation}
\Lambda_{i|i=\alpha} \le \hat \Lambda_{i|i=\alpha} =
 (\overline X_\beta-y)\exp\left(-\gamma (\overline X_i-\overline X_\beta)^2n_i\right)
 +(\overline X_\beta-B)\exp\left(-\gamma (\overline X_i-y)^2n_i\right)
\label{eqn:bound-twopart-hoeffding-alpha}
\end{equation}
If $y$ that minimizes $\hat\Lambda_{i|i=\alpha}$ exists, the minimum is achieved when
 $\frac {d\hat\Lambda_{i|i=\alpha}} {dy}=0$, that
is, when $y$ is the root of the following equation:
\begin{equation}
  2\gamma (\overline X_\beta-B)(\overline X_i-y)n_i = \exp\left(-\gamma \left(\frac {\overline X_i-\overline X_\beta}
    {\overline X_i-y}\right)^2n_i\right)
\end{equation}
The derivation for the case $i\ne \alpha$ is obtained by substitution $1-A, 1-\overline X_i, 1-\overline X_\alpha, 1-y$ instead of
$B, \overline X_i, \overline X_\beta, y$ into (\ref{eqn:bound-twopart-hoeffding-alpha}):
\begin{equation}
\Lambda_{i|i\ne\alpha} \le \hat\Lambda_{i|i\ne\alpha} = (y-\overline X_\alpha)\exp\left(-\gamma(\overline X_\alpha-\overline
  X_i)^2 n_i\right)+(A-\overline X_\alpha)\exp\left(-\gamma (y-\overline X_i)^2n_i\right)
\label{eqn:bound-twopart-hoeffding-rest}
\end{equation}
A closed-form solution for $y$ cannot be obtained, but given
$A, B, \overline X_\alpha, \overline X_\beta, n$, the value of $y$ can be efficiently
computed.

>>>>

\newtheorem{dfn}{Definition}
\newtheorem{thm}{Theorem}
\newtheorem{lmm}{Lemma}
\newtheorem{crl}{Corollary}

@@

The simple regret of a sampling policy for the Multi-armed Bandit
Problem is the expected difference between the best expected reward
$\max\limits_i\IE[X_i]$ and the expected reward $\IE[X_j]$ of the arm
with the best sample mean $\overline X_j=\max\limits_i\overline X_i$:
\begin{equation}
\label{eqn:simple-regret}
\IE[R]=\sum_{j=1}^K\Delta_j\Pr(\overline X_j=\max_i\overline X_i)
\end{equation}
where $\Delta_j=\max\limits_i\IE[X_i]-\IE[X_j]$.  Strategies that
minimize the simple regret are called pure exploration strategies
\cite{Bubeck.pure}. Principles of rational metareasoning
\cite{Russell.right} suggest that at each step the arm with the
greatest value of information (VOI) estimate must be pulled, and the
sampling must be stopped and a decision must be made when no arm has
positive VOI estimate.

@@

The probabilities in equations (\ref{eqn:thm-vopi}, \ref{eqn:thm-be})
can be bounded from above using concentration inequalities. In
particular, Theorem~\ref{thm:hoeffding-prob-bounds} (proved in 
Appendix~\ref{app:hoeffding-prob-bounds-proof}) is based on the
Hoeffding inequality (\ref{eqn:conc-hoeffding}):
\begin{thm} The probabilities in equations (\ref{eqn:thm-vopi},
\ref{eqn:thm-be}) are bounded from above as
\begin{eqnarray}
\Pr(\IE[X_i] \le \overline X_\beta|i=\alpha)&
   \le & \exp(-2 (\overline X_i - \overline X_\beta)^2 n_i)\nonumber\\
\Pr(\IE[X_i] \ge \overline X_\alpha|i\ne\alpha)&
   \le & \exp(-2 (\overline X_\alpha - \overline X_i)^2 n_i)
\label{eqn:probound-perf-hoeffding}
\end{eqnarray}
\vspace{-1.5\baselineskip}
\begin{eqnarray}
\Pr(\overline X_i' \le \overline X_\beta|i=\alpha) &
   \le & 2\exp\left(- 2\left(\frac {1+\frac {n_i} N} {1+\sqrt {\frac {n_i} N}}(\overline X_i - \overline X_\beta)\right)^2 n_i \right)
   \le 2\exp\left(- 1.37(\overline X_i - \overline X_\beta)^2 n_i \right) \nonumber\\
\Pr(\overline X_i' \ge \overline X_\alpha|i\ne\alpha) &
   \le & 2\exp\left(- 2\left(\frac {1+\frac {n_i} N} {1+\sqrt {\frac {n_i} N}} (\overline X_\alpha - \overline X_i)\right)^2 n_i \right)
    \le 2\exp\left(- 1.37(\overline X_\alpha - \overline X_i)^2 n_i \right)
\label{eqn:probound-blnk-hoeffding}
\end{eqnarray}
\label{thm:hoeffding-prob-bounds}
\end{thm}

\begin{crl} An upper bound on the intrinsic value of perfect information is obtained by substituting
(\ref{eqn:probound-perf-hoeffding}) into (\ref{eqn:thm-vopi}):
\begin{equation}
  \Lambda_i^p \le \hat\Lambda_i^p=\left\{
  \begin{array}{l l}
    \overline X_\beta\cdot \exp\left(- 2(\overline X_i - \overline X_\beta)^2 n_i \right) & \mbox{{\rm if} $i=\alpha$} \\
    (1-\overline  X_\alpha)\cdot \exp\left(- 2(\overline X_\alpha - \overline X_i)^2 n_i \right)  &  \mbox{\rm otherwise}
  \end{array} \right.
\label{eqn:bound-perf-hoeffding}
\end{equation}
\label{crl:bound-perf-hoeffding}
\end{crl}
\begin{crl}
An upper bound on the blinkered VOI estimate with ordering independent of $N$ is obtained
by substituting (\ref{eqn:probound-blnk-hoeffding}) into (\ref{eqn:thm-be}).
\begin{equation}
  \Lambda_i^b \le \hat\Lambda_i^b=\left\{
  \begin{array}{l l}
    N\frac {\overline X_\beta} {n_i}\cdot 2\exp\left(- 1.37(\overline X_i - \overline X_\beta)^2 n_i\right)
      & \mbox{{\rm if} $i=\alpha$} \\
    N\frac {(1-\overline  X_\alpha)} {n_i}\cdot 2\exp\left(- 1.37(\overline X_\alpha - \overline X_i)^2 n_i\right)
      &  \mbox{\rm otherwise}
  \end{array} \right.
\label{eqn:bound-blnk-hoeffding}
\end{equation}
\label{crl:bound-blnk-hoeffding}
\end{crl}
Estimate $\hat\Lambda_i^b$ can be viewed as a relaxation of the myopic VOI
estimate to longer sequences of actions, such that the VOI estimate is
positive for some of the actions. Better bounds can be obtained through tighter estimates on the
probabilities, for example, based on the empirical Bernstein inequality
(\ref{eqn:conc-empbernstein}) or through a more careful application of
the Hoeffding inequality (Appendix~\ref{app:better-hoeffding-bound}).

@@

Monte-Carlo tree search \cite{Chaslot.montecarlo} selects at each
search step an action that appears to be the best based on outcomes
of \textit{search rollouts}. Two different criteria are employed in
action selection during a rollout:
\begin{itemize}
\item at the first step, the value of partial
information should be maximized to minimize the \textit{simple} regret
of the selection at the current root node;
\item as the goal of sampling in deeper tree nodes is estimating the
value of a node, rather than selection, it makes sense to minimize
the \textit{cumulative} regret of the rollouts from the second step
onwards.
\end{itemize}

@@

The experiments compare the UCT algorithm \cite{Kocsis.uct} with
modified versions of UCT in which the samples at the first step are
selected according to their VOI estimates. Three blinkered VOI
estimates were used for the comparison:
\begin{description}
\item[VCT:] based on Hoeffding inequality (\ref{eqn:conc-hoeffding});
\item[ECT:] based on Hoeffding inequality with an intermediate point (see
Appendix~\ref{app:better-hoeffding-bound});
\item[BCT:] based on empirical Bernstein inequality
(\ref{eqn:conc-empbernstein}).
\end{description}
For simplicity, the bounds on probability for an unlimited number
of samples were used in the estimate formulas. The estimates where
computed as follows:
\begin{eqnarray}\
  \Lambda_i^{VCT}& =&\left\{
  \begin{array}{l l}
    \frac {\overline X_\beta} {n_i} \cdot \exp\left(- 2(\overline X_i - \overline X_\beta)^2 n_i\right)
      & \mbox{{\rm if} $i=\alpha$} \\
    \frac {(1-\overline  X_\alpha)} {n_i}\cdot \exp\left(- 2(\overline X_\alpha - \overline X_i)^2 n_i\right)
      &  \mbox{\rm otherwise}
  \end{array}  \right.\nonumber\\
  \Lambda_i^{ECT}& =&\min\left(\Lambda_i^{VCT}, \min_y\left\{
  \begin{array}{l l}
    \frac {\overline X_\beta-y} {n_i}\cdot \exp\left(-2 (\overline X_i-\overline X_\beta)^2n_i\right)
    +\frac {\overline X_\beta} {n_i}\cdot \exp\left(-2 (\overline X_i-y)^2n_i\right)
      & \mbox{{\rm if} $i=\alpha$} \\
\frac {y-\overline X_\alpha} {n_i}\cdot \exp\left(-2(\overline X_\alpha-\overline X_i)^2n_i\right)
    +\frac {1-\overline X_\alpha} {n_i}\cdot \exp\left(-2 (y-\overline X_i)^2n_i\right)
      &  \mbox{\rm otherwise}
  \end{array} \right.\right) \nonumber\\
  \Lambda_i^{BCT}& =&\min\left(\Lambda_i^{VCT},\left\{
  \begin{array}{l l}
    \frac {\overline X_\beta} {n_i}\cdot 2\exp\left(- \frac {(\overline X_i - \overline X_\beta)^2 n_i} {\frac {14} 3 \frac {n_i} {n_i-1}(\overline X_i - \overline X_\beta) + 2 \overline X_i(1-\overline X_i)} \right)
      & \mbox{{\rm if} $i=\alpha$} \\
    \frac {(1-\overline  X_\alpha)} {n_i}\cdot 2\exp\left(- \frac {(\overline X_\alpha - \overline X_i)^2 n_i} {\frac {14} 3 \frac {n_i} {n_i-1}(\overline X_\alpha - \overline X_i) + 2 \overline X_i(1-\overline X_i)} \right)
      &  \mbox{\rm otherwise}
  \end{array} \right.\right)
\label{eqn:emp-estimates}
\end{eqnarray}

@@

One search domain in which Monte-Carlo tree search based on the UCT
sampling policy has been particularly successful is playing the game Go
\cite{Gelly.mogo}. This series of experiments compares
the winning rate of UCT against VOI-aware policies (VCT, ECT, BCT)
in Go and investigates the effect of early stopping and sample
redistribution.

@@

\begin{figure}[t]
\centering
\includegraphics[scale=0.8]{bests-bw.pdf}
\caption{Go: best winning rate comparison}
\label{fig:best-winning-rate}
\end{figure}
Figure~\ref{fig:best-winning-rate} presents relative performance of
different VOI-aware policies depending on the number of samples per
ply by comparing the best achieved winning rates against UCT (again,
the lower the bar, the better is the policy). Both ECT (based on the
Hoeffding inequality with an intermediate point) and BCT (based on the empirical
Bernstein inequality) are better than VCT. The difference between ECT
and VCT is most prominent for smaller number of samples, and the
winning rate of ECT increases relatively slowly with the number of
samples. In contrast, BCT is worse than ECT and only slightly better
than VCT for smaller number of samples, but the winning rate rapidly
increases with the number of samples, and for 10000 and 15000 samples
per ply BCT is the best of the policies with the winning rate reaching
67\%.

@@

\section{Proof of Theorem~\ref{thm:hoeffding-prob-bounds}}
\label{app:hoeffding-prob-bounds-proof}

@@

Bounds (\ref{eqn:bound-perf-hoeffding}, \ref{eqn:bound-blnk-hoeffding}) have the form
\begin{equation}
  \Lambda_i \le \hat\Lambda_i=\left\{
  \begin{array}{l l}
    (\overline X_\beta-B)\exp\left(- \gamma(\overline X_i - \overline X_\beta)^2 n_i \right) & \mbox{{\rm if} $i=\alpha$} \\
    (A-\overline  X_\alpha)\exp\left(- \gamma(\overline X_\alpha - \overline X_i)^2 n_i \right)  &  \mbox{\rm otherwise}
  \end{array} \right.
\label{eqn:bound-generic-hoeffding}
\end{equation}
where $A$ is the upper bound on the posterior sample mean $\overline
X_i'$ if $i\ne \alpha$, $B$ is the lower bound on $\overline X_i'$ if
$i=\alpha$. For $i=\alpha$, the bound can be improved by selecting an
intermediate point $B < y < \overline X_\beta$ and computing the bound
as the sum of two parts: 
\begin{itemize}
\item $\overline X_\beta-y$ multiplied by the probability that
  $\overline X_i' \le \overline X_\beta$;
\item $\overline X_\beta-B$ multiplied by the probability that $\overline X_i'\le
  y$.
\end{itemize}.
\begin{equation}
\Lambda_{i|i=\alpha} \le \hat \Lambda_{i|i=\alpha} =
 (\overline X_\beta-y)\exp\left(-\gamma (\overline X_i-\overline X_\beta)^2n_i\right)
 +(\overline X_\beta-B)\exp\left(-\gamma (\overline X_i-y)^2n_i\right)
\label{eqn:bound-twopart-hoeffding-alpha}
\end{equation}
If $y$ that minimizes $\hat\Lambda_{i|i=\alpha}$ exists, the minimum is achieved when
 $\frac {d\hat\Lambda_{i|i=\alpha}} {dy}=0$, that
is, when $y$ is the root of the following equation:
\begin{equation}
  2\gamma (\overline X_\beta-B)(\overline X_i-y)n_i = \exp\left(-\gamma \left(\frac {\overline X_i-\overline X_\beta}
    {\overline X_i-y}\right)^2n_i\right)
\end{equation}
The derivation for the case $i\ne \alpha$ is obtained by substitution $1-A, 1-\overline X_i, 1-\overline X_\alpha, 1-y$ instead of
$B, \overline X_i, \overline X_\beta, y$ into (\ref{eqn:bound-twopart-hoeffding-alpha}):
\begin{equation}
\Lambda_{i|i\ne\alpha} \le \hat\Lambda_{i|i\ne\alpha} = (y-\overline X_\alpha)\exp\left(-\gamma(\overline X_\alpha-\overline
  X_i)^2 n_i\right)+(A-\overline X_\alpha)\exp\left(-\gamma (y-\overline X_i)^2n_i\right)
\label{eqn:bound-twopart-hoeffding-rest}
\end{equation}
A closed-form solution for $y$ cannot be obtained, but given
$A, B, \overline X_\alpha, \overline X_\beta, n$, the value of $y$ can be efficiently
computed.
